Holier Than Thou: Partisan Gap in the Consumption\\ of Pornography Online\thanks{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.}

### 2023-01-08 ms/adult.tex
update ms.

	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party}

@@

	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party}

>>>>

	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}

@@

	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
